---
title: "ps_4"
author: "Tate Green"
date: "2/24/2019"
output: html_document
---


```{r, echo=FALSE}
library(readr)
library(tidyverse)
library(gt)
library(dplyr)

orig <- read_csv(
  "ps_4_elections-poll-nc09-3.csv",
                 col_types = cols(
                   .default = col_character(),
                   turnout_scale = col_double(),
                   turnout_score = col_double(),
                   w_LV = col_double(),
                   w_RV = col_double(),
                   final_weight = col_double(),
                   timestamp = col_datetime(format = "")))

```


```{r}
dem <- orig %>%
  count(response) %>%
  filter(response == "Dem")
```

```{r}
diff <- orig %>%
  count(response) %>%
  spread(response, n) %>%
  mutate(rep_und = Rep - Und)

```

```{r}
diffval <- orig %>%
  filter(gender != gender_combined) %>%
  nrow()
```


```{r}
white <- orig %>%
  filter(race_eth == "White") %>%
  filter(file_race_black != "White") %>%
  nrow()
```

```{r}
rep_time <- orig %>% 
  filter(response == "Rep") %>%
  select(timestamp) %>%
  arrange(timestamp) %>%
  slice(1)

dem_time <- orig %>%
  filter(response == "Dem") %>%
  select(timestamp) %>%
  arrange(timestamp) %>%
  slice(1)

time_difference <- as.numeric(rep_time - dem_time)
```

There were `r dem$n[1]` respondents who supported the Democratic candidate.

There were `r diff$rep_und[1]` more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (gender and gender_combined). There are `r diffval` individuals for whom these variables have different values.

There are `r white` respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.

The first response of Rep came `r round(time_difference)`  minutes (rounded to the nearest minute) before the first response of Dem.

```{r, echo=FALSE}
library(readr)
library(tidyverse)
library(gt)
library(dplyr)
library(ggplot2)

orig <- read_csv(
  "ps_4_elections-poll-nc09-3.csv",
                 col_types = cols(
                   .default = col_character(),
                   turnout_scale = col_double(),
                   turnout_score = col_double(),
                   w_LV = col_double(),
                   w_RV = col_double(),
                   final_weight = col_double(),
                   timestamp = col_datetime(format = "")))

```

```{r make_chart, echo=FALSE, results="asis"}
orig %>%
  select(final_weight, response, race_eth) %>%
  mutate(race_eth = fct_relevel(race_eth, c("White", "Black", "Hispanic", "Asian", "Other"))) %>%
  group_by(race_eth, response) %>%
  summarize(total = sum(final_weight)) %>%
  filter(race_eth != "[DO NOT READ] Don't know/Refused") %>%
  spread(key = response, value = total, fill = 0) %>%
  ungroup() %>%
  mutate(all = Dem + Rep + Und + `3`) %>%
  mutate(Dem = Dem / all) %>% 
  mutate(Rep = Rep / all) %>%
  mutate(Und = Und / all) %>%
  select(-all, -`3`) %>%
  na_if(0) %>%
  gt() %>%
    tab_header(
      title = "Polling Results in North Carolina 9th Congressional District") %>%
    tab_source_note(
      source_note = "Source: New York Times Upshot/Siena Data") %>%
    cols_label(
      race_eth = "Race",
      Dem = "DEM.",
      Rep = "REP.",
      Und = "UND.") %>%
    fmt_percent(columns = vars(Dem, Rep, Und),
                decimals = 0)